---
title: "About Data Science"
format: html
editor: visual
editor_options: 
  chunk_output_type: console
---

## What do you think being a data scientist is about?

-   I think being a data scientist is about looking at data, putting it in to software to help analyze and interpret. Then communicate the conclusion to an audience.

## What differences/similarities do you see between data scientists and statisticians?

-   Until this class, I thought that they were "basically" the same because both statisticians and data scientist work with data. But no, knowing a little more I feel like data scientist are more in front of the consumers meaning they would be the ones to write the reports about the data. Where as statisticians are more in the background, they deal more in the theoretical part of working with the numbers.

## How do you view yourself in relation to these two areas?

-   I feel like I am neither a Data Scientist or Statistician. But as a math teacher I am finding myself increasing working with numbers and metrics. Data Science seems to be more of what resonates with me on a data to day basis.

## Chunk to determine the class, type, and structure of the object y

```{r}
y<-density(iris$Petal.Width)
```

```{r}
typeof (y)
str(y)
class(y)
is.vector(y)
```

## Chunk that uses the plot function of y and hides R code with echo

```{r}
#| echo: false
plot(y)
```
